%-------------------------
% Resume in Latex
% Author  : Eric Zhao
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Eric Zhao} & Email : \href{mailto:21zhaoe@protonmail.com}{21zhaoe@protonmail.com}\\
  \href{https://github.com/Dophin2009}{https://github.com/Dophin2009} & +1-610-504-8573 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Conestoga Senior High School}{Berwyn, PA}
      {GPA: 5.20 / 5.00 (Weighted), 4.00 (Unweighted)}{Aug. 2017 -- June 2021}
      \resumeItemListStart
        \resumeItem{Coursework}
          {AP Computer Science A, AP Computer Science Principles,
            Multi-Variable Calculus, AP Calculus BC, AP Statistics, AP Physics
            C: Mechanics, AP Physics C: Electricity \& Magnetism, AP Chemistry,
            AP Biology, AP World History, AP United States History, AP
            Psychology, AP Economics, AP United States Government \& Politics, AP
            English Language \& Composition, AP English Literature \& Composition}
        \resumeItem{Extracurriculars}
          {Computer Science Club, National Honor Society, Operation Smile, Key
            Club, Symphony Orchestra}
        \resumeItem{Honors}
          {National Merit Finalist, National AP Scholar, George Washington Book Award}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart

    \resumeSubItem{Languages}
      {Rust, Python, Typescript, Java, JavaScript, Go, SQL, Bash, HTML, CSS, LaTeX, R}
    \resumeSubItem{Technologies}
      {Git, Docker, Node.js, Webpack, ReactJS, Angular, Spring Boot, REST, MySQL, Unix, Linux}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Compilers Independent Study}{Sept. 2020 -- Present}
      {\href{https://github.com/Dophin2009/isc}{https://github.com/Dophin2009/isc}}{}

      Independent study course to learn about compiler infrastructure and programming langauge
        design. Currently building a basic compiler to transform a minimal C-like language into x86
        assembly, written in Rust.

    \resumeSubheading
      {Wikichan}{Mar. 2018 -- Present}
      {\href{https://github.com/Dophin2009/wikichan}{https://github.com/Dophin2009/wikichan}}{}

      Open-source browser extension that queries Wikipedia and displays a summary popup when
        hovering over a word or phrase. Built using ReactJS, RxJS, and Webpack.

    \resumeSubheading
      {StogaCS Infrastructure}{June 2019 -- Present}
      {\href{https://github.com/stogacs}{https://github.com/stogacs}}{}

      \resumeItemListStart
        \resumeItem{Sign-In Backend}
          {REST API to service the Computer Science Club's QR code-based sign-in system.  Built with
            Spring Boot, Hibernate, MySQL, and AWS EC2. \\
            \href{https://github.com/Dophin2009/stogacs-login}{\textit{https://github.com/Dophin2009/stogacs-login}}}
        \resumeItem{Sign-In Web}
          {Web client for users and administrators to sign in to club meetings by scanning a QR
            code. Built with Angular 8. \\
            \href{https://github.com/Dophin2009/stogacs-web}{\textit{https://github.com/Dophin2009/stogacs-web}}}
        \resumeItem{stogacs.club}
          {Official portfolio website for the club. Built with ReactJS and Webpack. \\
            \href{https://github.com/stogacs/stogacs.club}{\textit{https://github.com/stogacs/stogacs.club}}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------LEADERSHIP EXPERIENCE-----------------
\section{Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Conestoga Computer Science Club}{Berwyn, PA}
      {Co-President}{Sept. 2017 -- Present}

      \resumeItemListStart
        \resumeItem{Meetings}
          {Organized and engaged members in weekly meetings to share knowledge and collaborate on
            projects.}
        \resumeItem{Workshops}
          {Wrote and directed lectures and workshops on various topics, including text encoding
            techniques, functional programming, and REST APIs.}
        \resumeItem{Trips}
          {Coordinated and led one-day and overnight student-only trips to hackathons and
            competitions as far as Boston.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Huaxia Chinese School at Great Valley}{West Chester, PA}
      {Front Desk Administrator}{Sept. 2018 - June 2020}

      Managed instructor attendance and front desk logistics, assisted students and parents, and
        coordinated with school administrators.

  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
