\documentclass[letterpaper,11pt]{article}

\input{preamble}

\begin{document}
\rheading
  {Eric Zhao}
  {\email{eric\_c\_zhao}{brown}{edu}}
  {\href{https://github.com/mirryi}{https://github.com/mirryi}}
  {\phonenumber{1}{610}{504}{8573}}

\rsection{Education}
  \begin{rsectionlist}
    \rsectionitem
      {Brown University}
      {Providence, RI}
      {Ph.D. in Computer Science}
      {Aug. 2024 -- May 2029}

      \rsectiondesc{
        My work is in programming languages and formal methods for systems, advised by Nikos
        Vasilakis and Robert Lewis.
      }

    \rsectionitem
      {University of Michigan}
      {Ann Arbor, MI}
      {B.S.E. in Computer Science, GPA: 3.98}
      {Aug. 2021 -- May 2024}
      
      \rsectiondesc{
        \begin{rpointlist}
          \rpoint
            {Minor}
            {Asian Languages \& Cultures (Japanese)}
          \rpoint
            {Technical Coursework}
            {Formal Verification of Systems Software,
             Advanced Programming Languages,
             Category Theory, \\
             Model Checking,
             Compiler Construction,
             Operating Systems,
             Human-Centered Software \& Design,
             Computer Organization, \\
             Foundations of Computer Science,
             Data Structures \& Algorithms,
             Robotics Mechanisms,
             Modern Algebra,
             Linear Algebra, \\
             Discrete Mathematics,
             Probability,
             Multivariable \& Vector Calculus}
          \rpoint
            {Language Coursework}
            {Practicum in Japanese Translation,
             Academic Japanese,
             Third Year Japanese I \& II, \\
             Second Year Japanese I \& II,
             Anglo-Saxon (Old English),
             Creative Writing}
          \rpoint
            {Honors}
            {James B. Angell Scholar, William J. Branstrom Prize,
              Japanese National Honor Society, Japanese Language Award}
        \end{rpointlist}
      }

    \rsectionitem
      {Osaka Graduate University}
      {Osaka, Japan}
      {Visiting Student}
      {June 2023 -- Aug. 2023}

      \rsectiondesc{
        Participated in an two-month summer study abroad overseen by CET Academic Programs in Osaka,
        Japan. Completed an intensive advanced Japanese language course and lived in apartment
        accommodations with Japanese university students.
      }

    % \rsectionitem
      % {Conestoga Senior High School}
      % {Berwyn, PA}
      % {GPA: 4.00, SAT: 1570/1600}
      % {Aug. 2017 -- June 2021}
      
      % \rsectiondesc{
        % \begin{rpointlist}
          % % \rpoint
            % % {Coursework}
            % % {Multivariable Calculus, AP Calculus BC, AP Computer Science A, AP Computer Science
              % % Principles, AP Statistics, AP Physics C: Mechanics, AP Physics C: Electricity and
              % % Magnetism, AP Chemistry, AP Biology, AP Psychology, AP Macroeconomics, AP Microeconomics,
              % % AP World History, AP US History, AP US Government \& Politics, AP English Language \&
              % % Composition, AP English Literature \& Composition}
          % \rpoint
            % {Activities}
            % {Computer Science Club, National Honor Society, KEY Club, Symphony Orchestra}
          % \rpoint
            % {Honors}
            % {National Merit Finalist, National AP Scholar, George Washington Book Award,
              % Computer Science Scholar, Distinguished Honor Roll}
        % \end{rpointlist}
      % }
  \end{rsectionlist}

\rsection{Research}
  \begin{rsectionlist}
    % \rsectionitem
      % {Incremental Type-Checking with Holes}
      % {University of Michigan}
      % {Advisor: Cyrus Omar}
      % {Nov. 2023 -- Present}

      % \rsectiondesc{
        % Designing an approach to incremental bidirectional type checking by encoding
        % provenantial type information into a binding graph with holes that may be incrementally
        % updated through an action semantics similar to the Hazelnut calculus.
      % }

    \rsectionitem
      {Total Type Error Localization and Recovery with Holes}
      {University of Michigan}
      {Advisor: Cyrus Omar}
      {Oct. 2022 -- Jan. 2024}

      \rsectiondesc{
        Developed the \emph{marked lambda calculus}, a judgmental framework for principled
        localization of and recovery from type errors, combining key ideas from bidirectional and
        gradual typing. I formalized the system and mechanized it in the Agda proof assistant,
        proving that all the desired metatheorems are satisfied. \\

        \textsc{Paper and Artifact [Distinguished Paper Award]}:
        \begin{adjustwidth}{1em}{}
          \underline{E. Zhao}, R. Maroof, A. Dukkipati, A. Blinn, Z. Pan, C. Omar. 2024.
          \emph{Total Type Error Localization and Recovery with Holes}.
          Proc. ACM Program. Lang 8, POPL, Article 68 (January 2024), 28 pages.
          https://doi.org/10.1145/3632910
        \end{adjustwidth}
      }

    \rsectionitem
      {Zydeco: A Polymorphic Call-by-Push-Value Language}
      {University of Michigan}
      {Advisor: Max New}
      {Sep. 2022 -- Dec. 2022}

      \rsectiondesc{
        Contributed to the development of a polymorphic call-by-push-value (CBPV) language as an
        alternative intermediate representation for compiling functional programs and encoding
        stack-based calling conventions. I helped to formalize the bidirectional typing semantics of
        the language.
      }

    \rsectionitem
      {Compiling Functional Programs with Holes}
      {University of Michigan}
      {Advisor: Cyrus Omar}
      {Jan. 2022 -- Sep. 2022}

      \rsectiondesc{
        Explored the design space of compiling incomplete functional programs, i.e. programs with
        \emph{holes}. Designed a compilation scheme and runtime system for Hazel that targets
        WebAssembly, including static analyses to optimize the speed of operations with holes. \\

        \textsc{Abstract and Poster (2nd Place in Undergraduate Student Research Competition)}:
        \begin{adjustwidth}{1em}{}
          H. Chen, Y. Chen, \underline{E. Zhao}. 2022.
          \emph{Compiling Functional Programs with Holes}.
          ACM SIGPLAN International Conference on Functional Programming.
        \end{adjustwidth}
      }

    \newpage
    \rsectionitem
      {Hazel: A Live Programming Environment with Typed Holes}
      {University of Michigan}
      {Advisor: Cyrus Omar}
      {June 2021 -- Aug. 2022}

      \rsectiondesc{
        Assisted in the development of Hazel, a functional programming language and live programming
        environment capable of analyzing and evaluating incomplete programs. I worked to integrate
        primitive string type and expressions, built-in expressions, environment-based evaluation,
        live testing, and asynchronous evaluation for pedagogical uses of Hazel.
      }
  \end{rsectionlist}

\rsection{Teaching}
  \begin{rsectionlist}
    \rsectionitem
      {EECS 490: Programming Languages}
      {Ann Arbor, MI}
      {Instructional Aide (F23, W24)}
      {Aug. 2023 -- May 2024}

      \rsectiondesc{
        Teaching weekly discussion sections and conduct office hours for over 100 undergraduate
        students in an introductory course on programming language theory and design, covering
        topics from functional programming language semantics to imperative program verification and
        distributed computation models.
      }
  \end{rsectionlist}

\rsection{Awards}
  \begin{rsectionlist}
    \rsectionitem
      {NSF Graduate Research Fellowship}
      {National Science Foundation}
      {\$159,000, over 3 years}
      {Apr. 2024}

      \rsectiondesc{
        Awarded a fellowship of \$159,000 over 3 years for Ph.D. research in programming languages,
        compilers, and verification; one of 2,037 total awardees.
      }

    \rsectionitem
      {U.S. Department of Education Foreign Language and Area Studies Fellowship}
      {University of Michigan}
      {\$7,500, for Summer 2023}
      {Apr. 2023}

      \rsectiondesc{
        Awarded \$5000 in tuition and \$2500 in stipend for participation in the CET Academic
        Programs summer intensive language study abroad in Osaka, Japan.
      }

    \rsectionitem
      {Center for Japanese Studies Undergraduate Study Abroad Scholarship}
      {University of Michigan}
      {\$500, for Summer 2023}
      {Apr. 2023}

      \rsectiondesc{
        Awarded a \$500 stipend in addition to the Foreign Language and Area Studies Fellowship.
      }
  \end{rsectionlist}

\rsection{Certifications}
  \begin{rsectionlist}
    \rsectionitemthin
      {Japanese Language Proficiency Test N1}
      { \textsc{passed, 142/180}}
      {\textit{\small Jan. 2024}}
  \end{rsectionlist}

\rsection{Skills}
  \begin{rlinelist}
    \rline
      {Technologies}
      {C++, C, Rust, OCaml, Python, Java, Typescript, \LaTeX, Agda,
        Git, Docker, CI/CD, React, Linux, Unix}
      
    \rline
      {Languages}
      {English (native),
        Japanese (limited working proficiency),
        Mandarin Chinese (limited working proficiency)}
  \end{rlinelist}

\rsection{Service}
  \begin{rsectionlist}
    \rsectionitemthin
      {Student Volunteer}
      {, Midwest Programming Languages Summit (MWPLS) 2023}
      {\textit{\small Oct. 2023}}

    \vspace*{-1em}
    \rsectionitemthin
      {Student Volunteer}
      {, ACM SIGPLAN International Conference on Functional Programming (ICFP) 2022}
      {\textit{\small Sep. 2022}}
  \end{rsectionlist}

\rsection{Extracurriculars}
  \begin{rsectionlist}
    \rsectionitem
      {Japanese Language Circle}
      {University of Michigan}
      {Communications Chair}
      {May 2023 -- May 2024}

      \rsectiondesc{
        Handled communications with members and department administration, organized and facilitated
        conversation tables twice a week, coordinated with Japanese language instructors to conduct
        events in relation to Japanese language and culture.
      }

    \rsectionitem
      {IEEE Eta Kappa Nu (HKN), Beta Epsilon Chapter}
      {University of Michigan}
      {Member}
      {Sep. 2022 -- May 2024}

      \rsectiondesc{
        Engage in service activities, especially tutoring fellow students in introductory computer
        science and engineering courses.
      }
    
    % \rsectionitem
      % {Conestoga High School Computer Science Club}
      % {Berwyn, PA}
      % {Co-President}
      % {Sep. 2017 -- May 2021}

      % \rsectiondesc{
        % Organized members in weekly meetings, directed workshops on various topics, and led student
        % trips to competitions. Built digital infrastructure, including a QR code-based sign-in
        % system with Angular, Spring Boot, and MySQL.
      % }
  \end{rsectionlist}

% \rsection{Work Experience}
  % \begin{rsectionlist}
    % \rsectionitem
      % {Future of Programming Lab}
      % {Ann Arbor, MI}
      % {Research Assistant}
      % {June 2021 -- Present}
      
      % Formalising and implementing \href{https://hazel.org}{Hazel}, a functional programming
      % language and live programming environment capable of analysing and evaluating incomplete
      % programs, i.e. programs with holes, under Cyrus Omar.

      % \begin{rpointlist}
        % \rpointlone{Worked to integrate primitive string type and expressions, built-in expressions,
          % environment-based evaluation, live testing, and asynchronous evaluation for pedagogical
          % uses of Hazel, particularly in the course EECS 490: Programming Languages.}
      % \end{rpointlist}

    % \rsectionitem
      % {814 Interactive}
      % {Berwyn, PA}
      % {Software Development Intern}
      % {May 2021 -- June 2021}

      % Worked with React, Laravel Eloquent, and other web technologies to develop a tooling prototype
      % to ease the creation of location- and service-targeted website content and improve SEO for
      % local client businesses.

    % \rsectionitem
      % {Huaxia Chinese School at Great Valley}
      % {Exton, PA}
      % {Front Desk Administrator}
      % {Sep. 2018 -- June 2020}

      % Managed instructor attendance, assisted students and parents, and coordinated with school
      % administrators and facility staff.
  % \end{rsectionlist}

% \rsection{Other Projects}
  % \begin{rsectionlist}
    % \rsectionitem
      % {Wikichan}
      % {\small \itshape March 2019 -- Present}
      % {\small \url{https://github.com/mirryi/wikichan}}
      % {}

      % Using Typescript, React, RxJS, and modern web technologies, developed a cross-platform browser
      % extension that queries Wikipedia and displays a helpful summary popup when hovering over a
      % word or phrase.

    % \rsectionitem
      % {Compilers Independent Study}
      % {\small\itshape September 2020 -- May 2021}
      % {\small \url{https://github.com/mirryi/isc}}
      % {}

      % Engaged in an independent study course to learn about compiler infrastructure and programming
      % language design. Worked on building a basic compiler from scratch to transform a minimal
      % C-like language into x86 assembly, written in Rust.
  % \end{rsectionlist}
\end{document}
